validateHOT - Validate your Holdout Task

### 2023-11-11 paper/paper.Rmd
updated paper - 231111

| Validation metrics | Confusion matrix | Market simulations | Rescaling scores |
|:----------------:|:----------------:|:----------------:|:----------------:|
|     hitrate()      |    accuracy()    |    freqassort()    |    att_imp()     |
|        kl()        |       f1()       |     marksim()      |  prob_scores()   |
|       mae()        |   precision()    |      reach()       |    zc-diffs()    |
|      medae()       |     recall()     |       turf()       |                  |
|       mhp()        |  specificity()   |                    |                  |
|       rmse()       |                  |                    |                  |

@@

```{r}
# create holdout task and define relevant column indexes
HOT <- createHOT(
  data = MaxDiff, 
  id = "ID", 
  none = "none", 
  prod.levels = list(3, 10, 11, 15, 16, 17, 18), 
  method = "MaxDiff", 
  choice = "HOT", 
  varskeep = "Group"
)
```

>>>>

| Validation metrics | Confusion matrix | Market simulations | Rescaling scores |
|:----------------:|:----------------:|:----------------:|:----------------:|
|     hitrate()      |    accuracy()    |    freqassort()    |    att_imp()     |
|        kl()        |       f1()       |     marksim()      |  prob_scores()   |
|       mae()        |   precision()    |      reach()       |    zc_diffs()    |
|      medae()       |     recall()     |       turf()       |                  |
|       mhp()        |  specificity()   |                    |                  |
|       rmse()       |                  |                    |                  |

@@

```{r}
HOT <- createHOT(
  data = MaxDiff, 
  id = "ID", 
  none = "none", 
  prod.levels = list(3, 10, 11, 15, 16, 17, 18), 
  method = "MaxDiff", 
  choice = "HOT", 
  varskeep = "Group"
)
```
